Extending the WebID Protocol with Access Delegation

### 2012-08-03 paper.tex
fix some bib and list issues

\lstinputlisting[
    lastline=12,name=webid,style=turtle,float=htb,label=listing:webid1,
    basicstyle=\ttfamily\scriptsize,
    caption={Minimal WebID profile including a public key}
]{Listings/webid1.ttl}

\lstinputlisting[
    firstnumber=last,firstline=13,name=webid,style=turtle,float=htb,label=listing:webiddelegation,
    basicstyle=\ttfamily\scriptsize,
    caption={Access delegation by explicitly and implicitly identifying agents or application},
    label={list:sec_relation},
]{Listings/webid1.ttl}

\lstinputlisting[
    name=schema,style=turtle,float=htb,label=listing:schema,
    basicstyle=\ttfamily\scriptsize,
    caption={Schema description of the delegation property},
]{Listings/schema.ttl}\todo{A:why add the public key of the agent here? (revocation issues)}

\section{Evaluation}\label{sec:eval}

@@

>>>>

\lstinputlisting[
    lastline=13,name=webid,style=turtle,float=htb,label=listing:webid1,
    basicstyle=\ttfamily\scriptsize,
    caption={Minimal WebID profile including a public key and a secretary relation}
]{Listings/webid1.ttl}

%\lstinputlisting[
    %firstnumber=last,firstline=13,name=webid,style=turtle,float=htb,label=listing:webiddelegation,
    %basicstyle=\ttfamily\scriptsize,
    %caption={Access delegation by explicitly and implicitly identifying agents or application},
    %label={list:sec_relation},
%]{Listings/webid1.ttl}\todo{A:why add the public key of the agent here? (revocation issues)}

\lstinputlisting[
    name=schema,style=turtle,float=htb,label=listing:schema,
    basicstyle=\ttfamily\scriptsize,
    caption={Schema description of the delegation property},
]{Listings/schema.ttl}

\section{Implementation and Evaluation}\label{sec:eval}

@@

\section{Conclusion and Future Work}
